\documentclass[a4paper,11pt]{article}

% \graphicspath{{../pdf/}{../jpeg/}}
% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}

\usepackage{amsfonts, amsmath, amssymb, bm}
\usepackage{float}
\usepackage{url}
%\usepackage{hyperref}
\usepackage{subfigure}
%\usepackage{graphicx}
%\usepackage{subcaption}

%\newcommand{\bfnull}{\textbf{null}}

\begin{document}

\title{Towards the Planning of World Domination}
\author{Jason Gregory and Kamruzzaman Quddus}
\date{\today}

\maketitle

%
\section{Introduction}\label{sec:intro}
High-level overview of topic and introduction of problem statement: Warlight AI Challenge 2.

\subsection{Problem Statement}\label{sec:problem}
Describe rules of Warlight game (our bot vs one opponent, random map, fog of war, standard scoring and troop allocation, no cards).

\subsection{Previous Work}\label{sec:previous}
Reference other bots in challenge, publications on risk strategies, etc.

\subsection{Importance and Relevancy}\label{sec:importance}
What remains - Own implementation of planning algorithm using topics covered in this class.
Why interesting - Demonstrate topics from class in real-world example.
What is significance - Application of theoretical concepts to interesting game (and world domination)

%
\section{Technical Approach}\label{sec:approach}
High-level description of approach.

\subsection{Hypothesis}\label{sec:hypothesis}
We think a Refinement Acting Engine (RAE) will fit well into this structure and application.

\subsection{Process}\label{sec:process}
Describe how we plan to apply the RAE to this problem. 
High-level description of implementation. 
Evaluation will be via implementation and simulation (game engine).
Metric is (1) score compared to other bots and/or (2) score of each of our own implementations.

%
\section{Project Management}\label{sec:management}
High-level overview of milestones.

\subsection{Tasks}\label{sec:tasks}
Implementation components.

\subsection{Assignments}\label{sec:assignments}
Divide and conquer tasks, WAR code, etc.

\subsection{Schedule}\label{sec:schedule}
Gantt chart with milestones and dates.

%
\section{Conclusions}\label{sec:conclusions}
Summary of problem and intended approach.

% References 
%\bibliographystyle{plain}
%\bibliography{references}

% End document
\end{document}

